Add Plant Functional Type (PFT) labels

### 2021-04-05 R/add_plant_functional_type.Rmd
extracted the last word from each growth form

# simplify the growth form into "tree" or "shrub" 
cleaned_spectra_merged <- cleaned_spectra_merged %>%

@@

```{r}
# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(genusSpecies, growthForm) %>% 
    tally() 
```

>>>>

# simplify the growth form into "tree", "shrub", "saplng" etc.  
cleaned_spectra_merged <- cleaned_spectra_merged %>% 
  rowwise() %>%
  # parse out the last word in each entry's growthForm
  mutate(growthForm_simple = rev(strsplit(growthForm, " ")[[1]])[1])

@@

```{r}
# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(genusSpecies, growthForm_simple) %>% 
    tally() 
```
